\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\setlist{nosep}
\newcommand{\code}[1]{\nolinkurl{#1}}

\title{ParadePaard Frontend UI Rundown}
\author{A user-interface story}
\date{May 7, 2026}

\begin{document}
\maketitle

\section{Short Overview}

ParadePaard is a workforce application for employee planning, worked hours, travel claims, leave requests, payslips, account details, and company administration. From the frontend point of view, every active user starts from the same personal work area. They can manage their own shifts, worked hours, travel claims, leave, payslips, and account information according to the permissions they have.

Management access is now permission-based instead of being driven by one all-access mode. The frontend no longer decides the experience from a simple role flag. It loads the signed-in user's permission list and uses that list to show or hide management navigation, protect routes, and decide which actions are editable. A role named Admin can still exist, but it works like any other role: it grants a bundle of permissions. A user can also have narrower roles, such as planning manager, payroll reviewer, timesheet manager, or role manager, and the UI only exposes the pages and buttons connected to those permissions.

The app is held together by a top navbar, a permission-aware primary navigation rail, and route guards. The result is clearer: the dashboard is always the personal work dashboard, while management work lives under the Management area and is assembled from the user's actual permissions.
\section{Every Frontend Page and Screen}

\subsection{Root Entry Route}

The root route \code{/} is no longer a standalone home page. It now acts as the application's entry redirect. When someone opens the base localhost URL, the route first uses the same active-user guard as the dashboard. If the user is active, the frontend immediately redirects to \code{/dashboard}. If the user is not signed in, the guard sends them to \code{/login}. If the user is still in \code{PENDING_SETUP}, the guard sends them to onboarding instead.

This keeps the first browser entry point aligned with the rest of the protected app. A person who already has an active session lands on the operational dashboard, while a signed-out visitor is sent into the login flow rather than seeing a separate home screen.

\subsection{Login Page}

The login page is the normal entry point for signed-in users. It presents a compact form with a username field, a password field, a login button, and a link to the forgot-password page. If authentication fails, an error message appears inside the form area.

After the user submits the form, the frontend does more than simply accept a token. It loads the current user and decides where the user should go next. If the response says the password must be changed, the user is sent to the reset-password screen. If the user is still in \code{PENDING_SETUP}, the next destination is employee onboarding. If the user is already active, the next destination is the dashboard. This makes login the first decision point in the whole user journey.

\subsection{Forgot Password Page}

The forgot-password page gives the user a single email field and a button to send a reset link. There is also a simple Back link that returns to the login page. After submission, the screen changes to a confirmation message that tells the user a reset link will be sent if an account exists for that email address.

The UI keeps the flow intentionally simple. The user does not search for their account or answer extra questions. They only provide an email address and return to the login flow when finished. Reset emails are sent through the MailerSend Email API configuration, so the frontend keeps the same simple confirmation behavior while the backend uses the configured MailerSend token to deliver the message.

\subsection{Reset Password Page}

The reset-password page is used both for ordinary password recovery and for forced password changes after login. It shows two password fields: one for the new password and one to confirm it. The reset button is disabled if there is no token, and the page displays an invalid-link message when a reset token cannot be found.

The page validates that both password fields match before submitting. When the reset succeeds, the page shows a success message. If the user arrived here as part of another flow, the frontend refreshes their status and sends them back to the right next screen. This is why a newly invited employee can be forced through password reset first and then continue directly into onboarding.

\subsection{Public Application Page}

The public application page at \code{/apply} lets a person apply to work for ParadePaard without signing in. It is a practical application form rather than a marketing page. The page is separate from the protected employee and management areas, so an applicant can submit their first details before becoming an invited employee.

The page shows grouped sections for personal details, work interest, note, and confirmation. Personal details include full first names, preferred name, prefix, surname, email address, phone number, date of birth, gender, nationality, current city, and current country. Work interest includes role interest, contract preference, availability or start date, whether the applicant has worked for ParadePaard before, and an optional CV upload. The date of birth and availability or start date fields ask the applicant to enter dates as \code{dd/mm/yyyy}. When the applicant types digits into these fields, the slashes are added automatically so a date such as 03022000 becomes 03/02/2000.

The name fields now show Dutch-style placeholder examples to guide entry. Full first names shows \code{Jan Jeroen}, preferred name shows \code{Jan}, prefix shows \code{van}, and surname shows \code{Dijk}. These examples help applicants understand how to split a Dutch name across the separate fields.

The Note section gives the applicant one open text area for extra information. The application API stores this text as the applicant note, and reviewers see it as Note in the application detail page. The CV upload uses a styled file picker that shows a clearer Choose CV file action and the selected file name. The worked-for-us-before, contact-consent, and information-accurate checkboxes show the checkbox before the sentence so the choice reads clearly from left to right.

The user can fill in the required fields, choose a contract preference such as on-call, fixed hours, temporary event work, or no preference, add one optional note for the reviewer, attach a CV if they want, and submit the application. The submit action goes through the public application gateway route, so a visitor can apply from \code{/apply} without signing in. Before submitting, the user must confirm that ParadePaard may contact them about the application and that the information is accurate.

The application submit request now lets the browser manage the multipart upload headers itself. That keeps the CV upload and application data formatted correctly so the form can submit reliably through the gateway.

The page intentionally does not ask for sensitive onboarding information such as bank details, BSN or tax ID, identity document numbers, or ID images. After submission, the page shows an ``Application submitted'' confirmation and explains that sensitive onboarding information is only requested later if the application continues. If the applicant enters an email address that is already used by an existing application or user account, the application is not submitted and the form shows an email-already-exists error. If submission fails for another reason, the form shows an error message so the applicant can try again.

\subsection{Employee Onboarding Page}

The employee onboarding page is the first private self-service page for an accepted applicant or newly invited employee. It is built as a five-section card called Finish Your Setup. The sections are Address, Bank details, Payroll and tax, ID verification, and Emergency contact. The step indicator shows where the employee is in the setup flow.

The Address section collects street, house number, optional suffix, postal code, city, and country. The house number and suffix fields sit next to each other as separate input cells with clear spacing between them, so the user can tell where one value ends and the other begins.

The Bank details section collects the IBAN and the bank account holder name. The Payroll and tax section collects the BSN, optional nationality, one loonheffingskorting choice, and optional payroll notes. The step no longer asks the applicant to choose pension participation or the special Zvw contribution during setup.

The ID verification section collects the document type, document number, issue date, expiration date, issuing country, and two required ID document uploads: one for the front and one for the back. The issue date and expiration date fields use a dd/mm/yyyy text format and automatically add the slashes while the employee types. The two upload boxes sit next to each other on larger screens and stack on smaller screens. Each box now uses the same compact visual structure as the CV upload on the public application form, with a dashed drop area, a centered Choose file button, and the selected filename shown directly underneath the button. The ID upload flow accepts both image files and PDF files, and it also accepts the older single-file multipart shape so uploads keep working across backend builds that still serve the legacy request format. The Emergency contact section collects the emergency contact name, relationship, phone number, and optional email address.

The employee can move forward only after completing the required fields for the current section. The Back button lets the employee return to earlier sections. When the employee finishes setup, the frontend uploads both ID document images first and then submits the setup details. If either upload fails, the employee is returned to the ID verification section and sees a clear upload error so they can retry before the account moves into review. Pending setup employees can complete the ID document upload even if their temporary setup account is missing the normal onboarding permission in its token, as long as their own user profile is still in a setup state.

When setup and ID upload both succeed, the account moves to \code{PENDING_PROFILE_REVIEW}. The onboarding page then shows a waiting state explaining that the submitted onboarding details are awaiting internal review. A user who already has \code{PENDING_PROFILE_REVIEW} status also sees this waiting state instead of the form. The frontend no longer treats this review status as \code{ACTIVE}, so the employee is not sent to the normal dashboard before management review.

\subsection{Dashboard Entry}

The dashboard entry point now shows the personal User Dashboard for every active user. It is no longer split into a management dashboard and an employee dashboard. This makes the first signed-in page predictable: every user lands on their own work overview first.

Management work has moved into the separate \code{/management} area. Users who have at least one management permission see Management in the primary navigation and can open the management dashboard from there. Users without management permissions do not see that entry and are kept in the personal work flow.
\subsection{User Dashboard}

The User Dashboard is the employee's main overview page. It brings together the information an employee most likely needs when opening the app: their hours, leave balance, recent payslips, pending shift requests, accepted planning, and leave requests.

The General Information card summarizes the employee's worked hours for the current week, month, year, and all time. It also shows leave hours left, leave hours pending, and leave hours approved. The app uses a base leave allowance of 120 hours and subtracts approved leave from that allowance for the available leave display. If timesheet data cannot be loaded, the same card shows the timesheet error.

The Payslips card shows a compact table of payslips with date, week, function, hours, net amount, and actions. The employee can download a PDF directly from the table. If the employee thinks a payslip is wrong, they can open a report modal, enter a short title and optional note, and submit the error for payroll review. A payslip that is already disputed shows as Reported rather than showing the report button again. The View all button opens the full payslips page.

The My planning card is both an overview and an action area for active planning. Pending shift requests are shown first, but shifts that have already ended are not shown on the dashboard. Each request gives the employee the event name, date, time, function, and location. The employee can accept or decline current and future requests. Accepted shifts shown on the dashboard are also limited to current and future shifts. They are shown as one compact table with event, day, time, function, and a status pill for whether its timesheet is Scheduled or Logged. The table uses the full card width so the columns line up cleanly with the card edges. The list becomes scrollable when there are many shifts, so the dashboard card stays compact. Clicking a row opens the shift detail page. The View all button opens the full My Planning page, where the Past tab keeps completed shifts available for history.

The My leave requests card lists the employee's leave requests with date range, requested hours, status, and optional note. The New Request button opens the leave request modal, where the employee can create another leave request. The dashboard therefore acts as a daily command center for employees: it shows what is planned, what has been worked, what has been paid, and what still needs action.

\subsection{Messages Page}

The Messages Page lets an active user send messages to the company from one ongoing conversation. The page is meant to feel like one direct line to the ParadePaard company inbox, not like a list of separate admins or separate support tickets.

The page keeps the shared top navigation bar visible, consistent with the other personal pages, while the left side navigation shows the normal personal navigation items.

The page shows the message history in chronological order. Messages from the signed-in user are shown as the user's own messages, and replies from management are shown as Company messages. The user can type a new message and send it to the company. If there are no messages yet, the page explains that the user can send the first message to the company.

While the user stays on the page, the thread updates live. New company replies appear automatically without the user needing to manually refresh the page.

The live message stream now stays separate from the data loading used by the rest of the app. A user can leave Messages open for incoming replies without causing Account, Dashboard, or management user pages to fail while the stream waits for updates.

The page includes loading, empty, error, and sending states. After a message is sent, the conversation updates immediately so the user can continue in the same thread later.

\subsection{Management Dashboard}

The Management Dashboard is the entry page for permission-based company work. It does not assume the user has broad access. Instead, it reads the user's permissions and shows only the management areas the user can open from this dashboard.

A user with user-view access sees user management. A user with application-review access sees Applications. A user with onboarding access sees employee onboarding. A user with onboarding-review access sees the onboarding review queue. A user with contract access sees the contract workspace and the Horeca Payroll and Contract Rules card when the user also has company-management access. A planning manager sees planning and clients. A user with \code{CAN_VIEW_ALL_TIMESHEETS} sees the management Work history page. A timesheet manager sees travel claims. A payroll user with all-payslip or review permissions sees payslip pages. A company or role manager sees company settings and horeca payroll rule management. If a user has only one narrow management permission, the dashboard stays narrow and only points to that work.

Messages are still available to admins with \code{CAN_MANAGE_MESSAGES} through the shared inbox interface, but the Management dashboard does not show a Messages card.

The management tools are now organized into clear page sections, such as People, Planning, Payroll, Contracts, and Company. Each section contains polished action cards with a short label and a clearer description. The whole card is clickable, so the user can open a management area without aiming for a separate Open button. This keeps the page as a launcher, but makes it easier for the user to scan which kind of management work each card belongs to.

The main management work pages now include a generic Back control near the page title. The control first uses the user's real browser history, so a person who opens an employee from dashboard search returns to the dashboard or whichever page they came from instead of being forced to the Users list. If a management page is opened directly with no previous page available, the Back control uses a sensible management fallback.

This page replaces the old separate dashboard flow. The dashboard is now a permission-based launcher: it explains what management tools are available to the current user without exposing unrelated areas.
\subsection{Horeca Payroll and Contract Rules Page}

The Horeca Payroll and Contract Rules page is a management page for configuring horeca contract and payroll values before an employment contract is generated. The page is only for the horeca sector for now. It uses source-based rule data for the Horeca CAO 2025 2026, the 2026 horeca wage table, Belastingdienst payroll tax documents, employer premium rules, and Pensioenfonds Horeca en Catering pension premium information.

The page shows an overview of the business flow: the employee works at the horeca client, the payroll company is the legal employer, the client sends or approves worked hours, the payroll company calculates gross wage from contract settings and CAO rules, withholds employee payroll tax and pension, pays the employee net wage, pays tax and employer premiums to the Belastingdienst, pays pension premium to the pension fund, and invoices the client based on the contract terms.

The page includes source document tables, job presets, contract settings, wage rules, tax and payroll rules, pension rules, an example contract population, and a payroll calculator. Important values show a source label next to the value. Clicking a source label opens a source details panel with the document name, source URL, page number, effective date, and explanation.

The Job Presets section lets an admin manage reusable horeca role templates such as Bar employee, Runner, Waiter, Kitchen help, and Supervisor. A preset contains the job title, job function, function group, default hourly wage, default monthly wage, contract type, default hours, payroll period, pension setting, holiday allowance setting, vacation buildup setting, source, active state, and notes. The section now keeps the table compact by moving preset creation and editing into a popup form. A Create job preset button sits in the top-right corner of the section header, and each preset row uses symbol buttons for edit, enable or disable, and delete actions. The popup now uses the same dark tabbed wizard layout as Create project, with the same modal inputs, action row, and section switching so the job preset editor feels like the rest of the admin wizards. Popup overlays dim the whole screen so the background cannot still be clicked while a popup is open.

The Contract Settings section shows how the final onboarding review uses the presets. Admin chooses the Horeca CAO 2025 2026, chooses a job preset, and the app fills job title, job function, function group, wage, hours, payroll period, pension setting, holiday allowance setting, and vacation buildup rule. The gross hourly wage field now keeps the manual wage override reason directly underneath it, so the reason stays attached to the wage value the admin is changing. The section keeps the page focused on payroll setup inputs and no longer shows a commercial payroll billing rate field. It now also shows the shared travel allowance rate that the app uses as a horeca rules value for onboarding and travel claim estimates. Admin can manually adjust wage or settings. If the manual wage is below the horeca wage table value for the employee age and function group, the app shows a blocking error. If the wage is above the CAO wage table, the app shows an above-CAO warning.

The Payroll Calculator section now uses a higher-level horeca scenario form instead of asking the user to type tax and premium values by hand. The user enters the employee date of birth, start date, function group, contract type, hours per week, wage, loonheffingskorting choice, and whether pension applies. The page then derives monthly hours, payroll tax withholding, holiday allowance, vacation buildup, pension deductions, and employer premiums from the horeca rule data and official source documents. The wage can still be adjusted manually, and the calculator shows the required horeca hourly wage for the selected age and function group so the user can compare the entered wage with the source-backed minimum.
\subsection{Payroll Finance Page}

The Payroll Finance page is a management-only page for the business financial side of payroll. It is not an employee wage page. It is only visible to users with explicit payroll finance permission. The auth permission seed creates the payroll finance permissions and gives them to the built-in admin permission set so the Payroll Finance card can appear for the Sanne admin account.

The page shows a clear notice that client billing rates and payroll margin are internal business values. These values are not visible to employees and are not determined by the Horeca CAO or the Belastingdienst.

The page currently keeps only the Finance Overview. It shows summary cards for total client revenue, total employee gross wages, total employer costs, total payable to the Belastingdienst, total payable to the pension fund, total net wages paid, total margin before overhead, average margin percentage, missing billing rate count, and negative margin count.

The overview is now based on the actual finance records available to the frontend. It no longer shows a hard-coded January 2026 payroll run or fake employee shift assignments. When there are no approved payroll finance records, the page shows zero values and a clear empty-state message that no approved payroll finance records are available yet.

The Approved Payroll Runs section, Revenue Summary section, obligation explanation cards, Finance Settings section, adjustment audit log, and run breakdown side panel have been removed for now. This keeps the page from showing revenue, margin, or payroll obligations that are not backed by real data.
\subsection{Management Messages Page}

The Management Messages Page is a shared company inbox for users with \code{CAN_MANAGE_MESSAGES}. It shows user conversations that belong to the admin's company. Multiple admins with the permission can open the same inbox, see the same incoming user threads, and reply in the same conversation.

The page also keeps the shared top navigation bar visible, consistent with the rest of the management workspace.

The admin message UI works like a shared company inbox. It shows the same user conversations to all admins with message access, and replies are shared across admins so the conversation stays consistent.

The inbox starts as a list of messenger names. Each row shows the employee name, email address, latest message preview, and an unread count when there are messages waiting for admin review.

When an admin clicks a messenger name, the whole message box changes into that user's chat. The list is no longer shown beside the thread, so the selected conversation fills the message box. A Back to inbox button returns the admin to the name list.

Admins can type a reply in the selected thread and send it as the company. The frontend does not ask the admin to choose which individual admin account should receive the message. The backend still records which admin sent the reply, but the normal user sees the reply as a Company message.

While an admin keeps the shared inbox open, new incoming user messages and new admin replies appear automatically. This keeps the inbox list and open conversation thread in sync across multiple admins without a manual page refresh.

The shared inbox live stream now stays separate from the data loading used by other management pages. Admins can leave the inbox open for new messages without making employee lists, user profiles, or account screens run out of available data connections.

The page includes loading, empty, error, and sending states. The first version is a practical shared inbox and does not include separate subjects, attachments, assignments, or realtime typing indicators.
\subsection{Management Applications Page}

The Management Applications Page is a protected application-review area for users with application permissions. Users with \code{CAN_VIEW_APPLICATIONS} or \code{CAN_REVIEW_APPLICATIONS} can open the queue from the Management area. Users without those permissions cannot open the route or see the management card.

The queue shows submitted public applications in a practical review list. Each row shows the applicant name, email address, phone number, role interest, contract preference, submitted date, and application status. The page has loading, error, refresh, and empty states so the reviewer can tell whether applications are still loading, failed to load, or simply not waiting for review.

The user can open any application row to see the application detail page. The detail page groups the submitted information into personal details, contact details, work interest, experience, CV and documents, applicant confirmation, and internal review. It shows application JSON fields only and does not expose CV file bytes in the page data.

If the applicant included a CV file name, the detail page shows a Download CV action. The action requests the CV through the protected application CV endpoint and uses a browser blob download, so the reviewer can open or save the submitted CV without the bytes appearing in the normal application detail response.

For submitted applications, users with review permission can add an optional review note and choose Accept application or Deny application. After a decision, the page shows the returned status and makes clear when \code{decisionEmailSent=false} means the decision email is pending or may need manual follow-up. Applications that are already accepted or denied no longer show the accept and deny controls; the page instead shows the current status. Accepted applications now keep a Resend decision email action available for reviewers, so a reviewer can send a fresh account setup email if the applicant did not receive the original message. The resend button is spaced below the closed-decision message so the review section stays easy to scan. The resent message uses account setup wording instead of password reset wording.
\subsection{Management Users Page}

The Management Users page is the employee directory for users with user-view permission. It shows all users in a paginated table, with each row presenting the user's avatar or initials, name, user ID, email, position, roles, date added, and status.

The toolbar above the table helps an authorized user find a person quickly. They can search by name or email, sort by name, status, position, or date added, change the sort direction, filter by tenure, refresh the data, and move through pages. Clicking a row opens the detail page for that employee. The page is protected by \code{CAN_VIEW_USERS} rather than by a broad all-access route.
\subsection{Management User Detail Page}

The Management User Detail page is the complete company view of one employee for users with user-view permission. The top of the page works like a profile header. It includes a back button, the employee's name, a status badge, email, position, location, role count, and summary metrics such as recorded hours, upcoming shifts, and last timesheet.

The page is organized into Profile, Timesheets, and Planning tabs. The Profile tab shows personal information, work details, active contract details, employee tax profile, roles and access, address, onboarding evidence, emergency contact, and bank details. The onboarding evidence card shows the submitted ID document type, number, issue date, expiration date, issuing country, and an action to open the uploaded ID document image. The page shows loading, missing-file, and error states for that image. Bank details also show the bank account holder name, and the personal information area includes nationality.

The active contract card now also shows contract status, contract payment frequency, signature timestamps, finalization timestamps, employer signature name, and review comments. If a pending profile review employee does not yet have a current contract, a manager with contract-management permission can create a contract draft from this card by choosing or typing the role or function, contract type (Fixed hours, On-call Runner, or On-call Bar), start date, optional end date, gross hourly wage, payment frequency, and travel allowance. After the draft is created, it becomes the current contract on the page so the normal Send contract action appears, but the page does not send the email automatically. If the viewer has the right contract permissions, they can send a draft contract email to the employee, resend a contract email when the contract is already marked sent, finalize an employee-signed contract through an employer signing panel, or reject it with a review comment. The employer signing panel asks the manager to confirm the review, type their full legal name, optionally draw a signature, and then finalize and sign the contract. When the email is accepted for delivery, the page confirms that the contract email was sent. If email delivery fails, the page shows the failure instead of showing a false sent message. If the viewer also has role permissions, they can add or remove roles. If they have user-management permissions, they can save management fields that are editable for them.

The Timesheets tab shows summary cards and timesheet history for that employee. The Planning tab shows the employee's relationship to scheduled work and can link back into planning screens. The page therefore connects a person's account, contract, payroll setup, worked hours, and planning record, while individual actions remain controlled by permissions.
\subsection{Management Employee Onboarding Page}

The Management Employee Onboarding page starts the new-employee flow for users with onboarding permission. It presents one main employee details form. The authorized user enters identity and contact data such as preferred name, first names, prefix, surname, gender, date of birth, email, and mobile number. The form also asks whether the person has worked for the company before.

The same screen captures initial employment and contract information. The user selects a position or function, enters contract start and end dates, chooses contract type, selects the contract payment frequency, supplies or accepts a gross hourly wage, and chooses whether the employee has travel allowance. The travel allowance toggle now tells the admin that the kilometer rate follows the Horeca Payroll and Contract Rules page instead of being entered on this form. If the selected function already provides a wage, the wage field is disabled and follows that function wage. Date inputs are formatted as the user types. The production form offers normal payroll frequencies such as daily, weekly, biweekly, and monthly.

When the form is submitted, the result area shows the created username, temporary password, contract information if returned, and the onboarding email status. The onboarding invitation email is sent through the MailerSend Email API configuration. From a user-interface point of view, this page turns a candidate into an invited employee who can then log in, reset their password if required, and complete onboarding.
\subsection{Management Onboarding Review Page}

The Management Onboarding Review page is a focused queue for users with onboarding-review permission. It is separate from the employee creation form, so opening Onboarding review from the Management Dashboard no longer sends the user to the generic onboarding page.

The page shows employees whose setup or contract flow needs management attention. Each row shows the employee name, email address, onboarding status, date added, an action, and a contract download column. The status labels make the work clearer by showing items such as Profile review, Changes requested, Awaiting signature, and Contract review.

The user can refresh the queue and open an Onboarding Review form from any row. If a current contract or draft already exists for that employee, the same row also shows a Download action so management can fetch the contract PDF directly from the queue. Rows without a contract leave that download space empty. The Onboarding Review page is a dedicated review workspace and does not show general profile tabs such as Profile, Timesheets, Planning, or roles and access.

The Onboarding Review page starts with a clear header that explains the purpose: review employee information before creating and sending the contract. A compact employee summary card shows full name, email, phone number, position, status as a badge, and registered date. Each review section header (Personal information, Address, Identification, Bank details, Emergency contact, Tax information, and Contract setup) has a checkbox directly in front of the section name. When the admin checks a section, it becomes Complete. If required fields are missing for that section, the checkbox is disabled and a Missing line lists what still needs attention.

The main body is a set of scan-friendly review sections: personal information, address, identification, bank details (with IBAN highlighted when missing), emergency contact, and tax information shown as simple Yes/No rows. The identification section shows the submitted document details and separate actions to open the front and back ID document uploads. If either side is missing, the section lists exactly which side still needs attention. Contract setup now clearly separates employee-provided information from admin-selected contract information. Employee-provided information includes identity, address, bank, identification, emergency contact, and tax choice from the onboarding profile. Admin-selected information includes the Horeca CAO 2025 2026, job preset, job title, job function, function group, contract type, start date, optional end date, hours, hourly wage, monthly wage when applicable, payroll period, work location, loonheffingskorting setting, pension setting, holiday allowance setting, manual wage override reason, and travel allowance. The travel allowance control now includes a short note that it is only a yes or no choice on this page and that the current rate is EUR 0.23 net per kilometer from the Horeca Payroll and Contract Rules page, not from this review form.

The Contract setup section includes a Job preset dropdown. Selecting a preset fills the job title, job function, function group, default wage, contract type, hours, payroll period, pension setting, holiday allowance setting, and vacation buildup rule. The admin can still adjust the wage or settings manually. If a manual wage is lower than the official horeca wage table amount for the employee age and function group, the page blocks contract creation and shows the error in the review checklist. If a wage is higher than the official wage table amount, the page allows it and shows an above-CAO warning. Important wage, holiday allowance, vacation buildup, hours, tax, and pension values show source labels. Clicking a source label opens a source details panel with the source document, URL, page number, effective date, and explanation.

The contract setup choices for Full time, Part time, and Zero hours now create the stored contract type correctly when the admin creates or sends a contract. This means the review form can use the horeca wording that managers see on screen while the contract record is saved as the correct fixed-hours or on-call contract type.

If the page already has a current draft contract, the contract action switches from Create contract draft to Update contract draft. This lets management change values such as gross hourly wage and save those edits back onto the existing draft instead of failing because a contract already exists. The Create and send contract action also uses the latest edited contract setup values before sending the contract email.

Accepted application users and their onboarding review data are kept when the services restart. This means an admin can accept an application, wait for the employee to finish setup, and then continue the Onboarding Review page without the employee disappearing or the page showing a no-user-found error because of startup seed data.

At the bottom, a Final review decision section lets the admin choose Ready to send contract, Needs changes, or Reject onboarding, enter an admin note, download the current contract PDF when a draft or current contract already exists, and run actions to save the review, request changes, create or update the contract draft, or create and send the contract. Saving the review updates the employee status so Needs changes moves the person to Changes requested, and Ready to send contract moves the person to Contract review. Saving the review also stores which review sections were checked and the contract setup draft fields so the onboarding review can be reopened later and continued from the same state. After the draft is created or updated, the same final review area immediately shows the download button for that contract. After Create and send contract sends the email, the employee status changes to Awaiting signature. The Create and send contract action is only available when all review section checkboxes are marked complete. If required fields are missing, the page blocks sending and shows a clear message listing what still needs to be completed.
\subsection{Management Contracts Page}

The Management Contracts page is the contract workspace for users with contract permissions. It is separate from the user directory, so opening Contracts from the Management Dashboard no longer sends the user to the general users list.

The page shows contract rows with employee name, function, contract status, start date, end date, and an action. A status filter lets the user switch between all contracts, contracts needing review, draft or sent contracts, finalized contracts, and rejected or expired contracts. Contract statuses are displayed in readable labels instead of raw database values. The Contracts page is only part of the management workspace. Employee self-service permissions for viewing or signing a person's own contract do not show this page or the Management navigation.

The user can refresh the contract list and open the related employee profile from any contract row. The employee profile contains the active contract card, PDF download, send or resend email, finalize, and reject actions when the user's permissions allow those actions. Contract PDF generation now has the correct service connection in Docker, so downloading a contract from the profile can fetch the employee profile data needed to build the PDF. Stored contract PDFs no longer prevent the active contract card from loading, so managers can still see the current contract details and actions after a PDF has already been generated.

Contract rows are kept when the contract service restarts. Management users can return to the Contracts page after a rebuild or restart and still see draft, sent, signed, finalized, and rejected contracts that were already created.
\subsection{Account Layout}

The Account page is a layout wrapper for personal account pages and company settings. It shows the shared navbar, a back button, a page title, side navigation, and the active account content. The personal account side navigation contains Personal info, Bank details, and Employment details. Users with company or role-management permissions can also open Company settings.

The account layout loads the current user and passes common account data to the nested account pages. It also owns the profile-picture upload and removal behavior used by the Personal info page. Company settings are no longer tied to a separate admin/personal switch; they are shown only when the signed-in user has the permissions needed for company or role configuration.
\subsection{Account Personal Info Page}

The Personal Info page displays the user's identity, contact information, and address. The first part of the page is the profile picture area. If the user has uploaded a picture, it appears in the avatar circle. Otherwise the page shows the user's initial. The user can upload, change, or remove their profile picture from this screen.

Below the avatar area, the Personal information card shows full name, preferred name, first names, middle name prefix, last name, gender, date of birth, email, and mobile number. The Address card shows street, house number, house number suffix, postal code, city, and country. These data fields are read-only in this account view. The main interactive part of the page is profile-picture management, and the navbar avatar updates when the picture changes.

\subsection{Account Bank Details Page}

The Bank Details page is intentionally minimal. It shows the user's IBAN inside a Bank details card. There is no edit form or save action on this page. For the user, this screen answers a simple question: which bank account is recorded for payroll and contract purposes?

\subsection{Account Employment Details Page}

The Employment Details page shows the user's current employment setup and current contract. It displays position or function, gross hourly wage, contract start date, contract end date, holiday allowance, payment frequency, profile status, contract status, and whether the user worked for the company before. If the contract has no end date, the page shows it as open-ended.

The main actions on this page are Contract PDF download and opening the contract signing flow. If a current contract exists, the user can download it from the Contract PDF row. Contract PDF download uses the contract service together with employee profile data from the user service, so the downloaded document can include the employee name, address, phone contact when available, contract terms, and signature information. The downloaded PDF now uses the same English employment agreement text that the employee reviews before signing. Downloads regenerate the stored PDF before returning it for draft, sent, and employee-signed contracts, so older cached Dutch contract PDFs are replaced before finalization. After management finalizes and signs the contract, the final PDF is kept as the locked signed document and the download returns that stored final PDF instead of regenerating it. Signed contracts include separate employer and employee signature blocks. Each block places the drawn signature above its own signature line, then shows the typed signature name and signed date underneath. If the contract is waiting for employee signature, the user sees a Review and sign contract button. That button opens the separate contract signing page instead of signing directly from employment details. Below the current details, the page shows a compact contract history with date range, payment frequency, and status for each contract. Current contract details continue to load after a PDF has been generated for the contract. If the contract cannot be loaded or downloaded, the page shows an error message.

\subsection{Contract Signing Page}

The Contract Signing page is a dedicated employee page at \code{/contracts/:contractId/sign}. It is used when an employee receives a contract email or opens the signing action from Employment Details. The page is separate from the normal employment details page so the employee reviews the contract as a document before signing.

The contract email button points directly to this route. If the backend is still configured with the older Employment Details URL, the email link is still converted to the correct contract signing route so employees do not land on a broken nested account URL. The frontend also redirects the old nested contract URL to the dedicated signing page, so an already-sent email with the old nested path can still open the contract page.

The main area shows a clean employment agreement preview. The contract is written with headings, numbered sections, and paragraphs instead of raw field names. Employee details such as name, address, email, phone number, position, wage, start date, end date, working hours, holiday allowance, leave entitlement, and travel allowance are inserted naturally into the contract text. When travel allowance applies, the wording now points the employee to the Horeca Payroll and Contract Rules instead of generic company policy wording. Company details are shown as ParadePaard employer details in the agreement.

The signing panel at the bottom or side of the page shows contract status, contract version, signed date if available, and typed signature name if already signed. Before signing, the employee must check the agreement checkbox that says I have read the employment contract and agree to it. The employee must also type their full legal name. The page checks the typed name against the employee name when that name is available. The employee can optionally draw a signature with a mouse or touch in the signature box.

The Sign contract button stays disabled until the contract is loaded, the agreement checkbox is checked, and the typed name is valid. When the employee signs, the app saves the signed status, signed date and time, signed user, typed signature name, optional drawn signature image, agreement checkbox text, contract version, document hash when available, browser user agent when available, and IP address when the backend can read it. The downloadable PDF is refreshed after signing so the employee receives the final contract with the signature section filled in at the bottom. The backend allows the owner of the sent contract to sign it even if their permission token is missing the explicit sign-contract authority, while still blocking non-owners and contracts that are not waiting for signature. After signing, the page locks the signing controls. The employee can still view the signed contract, but cannot edit or sign it again.

\subsection{Company Settings Page}

Company Settings is a multi-tab management area inside the account layout. It is the place where authorized users manage company identity, access roles, and workflow settings.

The Company details tab shows the company logo, company name, and company ID. The logo can be uploaded, changed, or removed. The company name can be edited by users with company-management permission, while the company ID is shown as read-only information. Saving company details updates the company information and refreshes navbar company display through a frontend event.

The Roles and permissions tab is a full role-management interface. The page shows existing roles with color dots and member counts. Creating a role happens in a modal with a Details step, a Permissions step, and a Members step. Editing a role uses a similar modal, but adds a Delete tab. A role has a name, color, permission set, and assigned members. The Permissions step groups checkboxes into sections such as Role access, People, Planning, Timesheets and travel, Payslips, Company settings, and Other. Each section shows how many permissions are selected, so the user can scan the permission catalog without reading one long flat list. The member tools include user search, selected member display, add actions, and remove actions. Deleting a role requires typing the role name for confirmation. Each operation is permission-gated, so a user may be able to assign members without being able to delete a role, depending on their permissions.

The Workflow settings tab controls company-wide operational behavior. It now shows only the timesheet logging mode and travel claim mode, because employee payment timing is already tied to the binding contract and does not need a separate company-wide payslip timing field. Timesheet logging can be set to admin finalization or automatic logging after shift end. Travel claims can require approval or be auto-approved.

\subsection{Management Planning Overview Page}

The Planning Overview page is the planning workspace for operational scheduling. It now gives the planner two main tabs: Shifts and Projects, and it opens on the Shifts tab by default. The top of the page shows the current period, previous and next controls, a Calendar view or List view selector, a Today button, a Weekly or Monthly selector, the Shifts and Projects tab control, a search field, and a Create project button.

The week or month selector controls the visible date range, the Calendar view or List view selector controls the layout, and the Shifts or Projects tabs control which kind of planning entries are shown. That means the planner can combine both controls: calendar shifts, calendar projects, list shifts, or list projects.

In weekly view, the page lays out days of the week. In monthly view, it shows a calendar grid. The shift cards show the title, a supporting subtitle, time information, client tag, and staffing ratio. Staffing is shown as required, scheduled, and checked in, and the visual tone changes when a shift is empty, partially staffed, or staffed.

The search field sits next to the Shifts and Projects tabs. The planner can search by assigned user, client, or project. The page then only shows matching project or shift cards within the current week or month.

Shift cards are selectable. Clicking a shift selects it. Holding Shift while clicking other shift cards adds or removes shifts from the current selection. Selected shifts show a clear highlighted state so the planner can see what is selected even after a menu is closed.

Clicking the main body of a selected shift opens a compact pop up menu near that shift. When one shift is selected, the menu offers Plan someone in and View shift details. When multiple shifts are selected, the menu offers Plan someone in and View selected shifts. Clicking outside the menu closes it, but the selected highlight remains.

Plan someone in opens a small planning panel in the same pop up. The panel starts empty and only searches employees once the planner types a name or email, so it does not load every user up front. Selected people appear as removable chips above the search results so the planner can keep track of the selection while continuing to search. The results list scrolls when many matches exist and supports long names with horizontal scrolling. The planner can then plan the selected people into all selected shifts at once. The page updates immediately after planning so staffing counters and shift states stay accurate without a manual refresh.

The planning calendar now stretches to the available browser height. This lets the day cells fill the screen so the white day columns continue down to the bottom of the planning area instead of ending early with empty background below them.

Creating a project happens through a multi-step modal. In the Details step, the planner enters the project name, start date, end date, default start time, default end time, and time zone. In the Client step, the planner selects the client/company and location. In the Notes step, the planner enters internal notes and reviews the project summary. The frontend validates the project name, dates, times, and time zone before creating the project. After creation, the overview reloads and focuses the relevant period while keeping the current Shifts or Projects tab selection.

If the planner creates a new project before adding any shifts, the page still stays usable. The new project can load without showing any shift rows yet, and the overview no longer crashes or turns into a white screen just because the project does not have planning days or shift data yet.

\subsection{Management Planning Clients Page}

The Clients page is the planning address book. It stores the client companies and contacts that can be attached to events. The table shows client image or initials, client name, contact count, address, and company line. A search field lets the planner search clients and contacts, and pagination controls handle larger client lists.

Adding or editing a client happens in a modal. The modal contains client profile details, an optional profile picture, address, company line, contacts, notes, and a summary. Contacts can be added or removed, and each contact has first name, last name, position, email, and phone fields. Contact rows can be expanded and collapsed. The client picture upload accepts image files, with the UI expecting PNG, JPG, or WEBP and enforcing a 500 KB size limit.

The page's main user flow is simple: the planner searches for a client, opens the client detail modal, updates company or contact details, and saves. Those client records can then be used when creating or editing planning events.

\subsection{Management Planning Event Detail Page}

The Event Detail page is where planning becomes concrete. The page opens one event and shows its shifts, staffing level, client information, timing, location, and notes. The main card title combines the event name and context, while the right side shows an event-level staffing requirement ratio.

The page is available from the Management Planning Overview page by opening an event card, and it can also be accessed directly at \code{/management/planning/events/:eventId}.

The page is split into a main shift area and a side event-details panel. The event-details panel shows client, client line, location, dates, default time, time zone, staffing summary, status, and notes. The edit button opens the event edit modal, where the planner can change event name, client, dates, times, time zone, location, internal notes, external notes, and summary. The modal also includes event deletion, with a browser confirmation before deleting.

The shift list is the main working area. A shift card shows the shift date, weekday, time, display name, function, staffing, duration, location, and the required/scheduled/checked-in ratio. The planner can create a shift, edit a shift, or delete a shift. The create and edit shift modals use the same core fields: start date and time, end date and time, job function, shift name, people needed, break minutes, and location.

When a shift is expanded, the planner sees two columns. The Scheduled people column shows current assignments and can be filtered by All, Scheduled, Accepted, or Declined. Assignment cards show the employee, status badge, and action buttons. A declined employee can be invited again. An active assignment can be removed. The Available people column lets the planner search active employees and schedule them into the shift. If there are many available people, the page shows only the first 50 and asks the planner to search.

The event can also be finalized. When the event is finalized, the frontend labels it as Finalized and disables create, edit, schedule, invite, and remove controls.

\subsection{My Planning Page}

The My Planning page is the employee's full planning page. It expands the planning card from the dashboard into a larger view with an Upcoming/Past toggle and an Accepted shifts list. Upcoming is for current and future planning. Past is the place where shifts that have already ended remain available for history.

Scheduled shifts are assignments with status \code{ASSIGNED}. These are requests waiting for the employee's response. When there are scheduled shifts waiting for a response, each one appears as a response card above the accepted shifts list. Each card shows event name, shift date, time, function, and location, and the employee can accept or decline it from actions on the right. If the request is already in the past, the page still displays it for history, but the buttons are disabled. If there are no scheduled shifts waiting for a response, the page does not show a scheduled section or an empty-state message.

Accepted shifts are assignments with status \code{CONFIRMED}. They are shown in the same table-style layout as the dashboard planning card. The table header sits directly under the card header, and the list is scrollable when there are many accepted shifts. Columns show event (with shift name or function as a second line), day, time, location, and a timesheet status pill. Future shifts show Scheduled. Past accepted shifts that have not become timesheets show Pending log. Shifts already exported or recorded as timesheets show Logged. Clicking an accepted shift opens the shift detail page.

\subsection{My Planning Shift Detail Page}

The My Planning Shift Detail page shows one shift assignment from the employee's point of view. The first card is the shift overview. It shows event name, date, time, shift name, function, location, break minutes, timesheet state, internal notes, and external notes. The back button returns the user to My Planning, preserving the past/upcoming context where relevant.

The second card is the travel claim area. It is only usable after the shift has ended. Before that, the page tells the employee that travel claims become available after the shift. Once available, the employee can enter kilometers traveled, upload a proof image, see the rate of EUR 0.23 per kilometer, view the calculated amount, and submit the claim. If a proof image already exists, the employee can open it. If a claim was rejected, the review note appears on the page.

The travel claim card uses a dedicated stacked form layout with a file-picker control, clear status and amount summary blocks, and a mobile-friendly layout so the proof upload and review state stay readable on smaller screens.

This page connects planning to expense reimbursement. The shift is first planned and accepted, then after completion it can produce a travel claim that later appears in review and work history.

\subsection{My Work History Page}

The My Work History page at \code{/work-history} shows the signed-in user's own logged timesheets. It is a personal history page, so it does not switch into an all-employee view even when the user also has management permissions.

The main content is a My timesheets card with a filter panel, table, total bar, and pagination. The filter panel uses flexible filter rows. The user chooses what to filter on, enters the value, and can add more filters with the Add filter button. The personal page can filter by search text, function, project, shift, date range, week year, week number, hours, travel amount, and finance readiness when the user's permissions allow those labels. The Reset filters button clears the filter state.

The My Work History page uses the default personal columns and does not show a column picker. This keeps the personal history page simple and focused on the user's own shifts, hours, travel, and visible finance readiness labels.

The table rows are clickable and keyboard-accessible. Opening a row sends the user to the worked shift detail page. At the bottom, the page shows total hours for the currently visible filtered data and pagination controls for page number and page size.

\subsection{Management Work History Page}

The Management Work History page at \code{/management/work-history} shows all logged company timesheets. It is only available to users with \code{CAN_VIEW_ALL_TIMESHEETS}. The Management Dashboard shows a Work history card only for users with that permission.

The page has the same work-history table pattern as the personal page, but it is designed for company review. It includes the employee column, can filter by employee, and has a Travel Claims shortcut in the header when the user also has timesheet-management permission.

The filter panel is built from flexible rows. A manager chooses a field in the Filter on dropdown, enters the value, and can add more filters. This means the manager can combine filters such as employee, function, date from, minimum hours, project, shift, week number, travel amount, or finance readiness instead of using one fixed set of always-visible fields.

The management page includes a scrollable column chooser. A manager can choose operational columns such as date, employee, shift, hours, travel, and finance readiness. Users with payroll finance permission also get finance-only columns such as billing rate source, client billing rate per hour, billing override reason, and finance lock status. These finance-only columns are not available to users without finance permission.

The selected management columns are saved to the signed-in user's account. When that user returns to the management Work History page, the same column selection is restored. If a saved column is no longer available to the user, the page falls back to valid default columns.

\subsection{Worked Shift Detail Page}

The Worked Shift page explains one logged timesheet in detail. The Shift overview card shows employee, date, time, shift, project, function, hours worked, break, timesheet state, and logged-at time. If the timesheet is linked to a planning assignment, the page loads that assignment too, so the displayed project and shift context can be richer than the timesheet alone.

When a user opens a worked shift from My Work History, the Back control returns to \code{/work-history}. When a user opens it from Management Work History, the Back control returns to \code{/management/work-history}. This keeps personal history and management history separate while using the same detail page.

The Travel expenses card shows the travel amount stored on the timesheet, submission status, kilometers, rate, submitted-at time, reviewed-at time, claim amount, and review note. If the claim includes proof, the page shows a View proof button. Users with all-timesheet or manage-timesheet permissions use management proof access, while employees use their own assignment proof access.

This page is mostly read-only. Its job is to let the user understand how a shift was recorded and how its travel expense was handled.

\subsection{Travel Claims Page}

The Travel Claims page is a review queue for pending travel claims. It shows a list of claims with employee, event, kilometers, amount, date, shift name or function, and location. If a proof image is attached, the reviewer can open it.

The page header now keeps navigation simple with only the standard Back control. There is no separate Back to work history shortcut in the header. The reviewer can approve the claim directly, or reject it. Rejecting uses a prompt where the reviewer enters the rejection reason. After approval or rejection, the claim is removed from the pending list. This page is therefore the manager side of the employee travel claim flow that starts on the shift detail page.

\subsection{Payslips Page}

The Payslips page is the main list for payroll documents. Employees see their own payslips. Users who can view all payslips can switch between My payslips and All payslips. The list shows date, user when in all scope, week, function, hours, net pay, status, and an action column. Scheduled payslips are now based on the active finalized contract and its payment frequency.

The page includes a detailed filter panel. Users can search, filter by status, choose date range, choose week year and week number, and filter by minimum or maximum hours and net pay. The special status filter \code{NOT_ACCEPTED} is a frontend convenience for focusing on payslips that are not released or approved. It is used from payroll review flows to quickly find problematic payslips.

The user can download a payslip PDF from the list, open a detail page by selecting a row, reset filters, and use pagination. For employees, this is a payroll archive. For payroll and management users, it is also a review and troubleshooting entry point.

\subsection{Payslip Detail Page}

The Payslip Detail page is the readable payslip view. The page header uses the standard Back control above the page title, and there is a separate Download PDF button. The hero summary shows employee name, function, week, issue date, available date, status badge, payslip ID, and key metrics for hours, gross amount, and net amount.

The rest of the page is organized into cards, but the information is shown in a list view instead of separate field tiles. Each card uses a simple two-column list (Item and Value). The Overview card lists issue date, week, available-to-user time, generated-at time, status, and payslip ID. The Pay details card lists function, hourly wage, hours worked, loonheffing, total deductions, travel expenses, gross total, and net total, with gross and net totals visually highlighted. The Deductions card shows a list with Deduction, Category, and Amount columns. The Deduction column shows the label, or falls back to the code when no label is available. The Employee details card lists name, user ID, date of birth, start date, address, and country. Payslips can now carry contract snapshot fields such as contract id, contract type, payment frequency, contract dates, weekly hours, and holiday allowance, so payroll reviewers can see what contract rule produced the period.

The page is read-only except for downloading the PDF and navigating back. Its role is to explain the payslip calculation to the user in a structured way.

\subsection{Management Payslip Detail Page}

The Management Payslip Detail page supports two different permission levels. A user with all-payslip view access can open the page, inspect the payroll information, download the PDF, and compare the payslip against related timesheets. A user with \code{CAN_MANAGE_PAYSLIPS} gets the editable payroll controls and the Save changes action.

The Overview card shows payslip ID, issue date, week, available-to-user time, and generated-at time. The Error handling card shows status, error title, and error note. The Pay details card shows function, hourly wage, hours worked, and travel expenses. The gross, loonheffing, deductions, and net amounts are shown as calculated summary values.

When the user has manage permission, those fields can be edited. The Deductions card becomes a line editor where each line can have code, label, category, calculation type, configured value, manual override, sort order, notes, and calculated amount. Users without manage permission see the same information in a disabled, view-only state and get a short notice that editing requires the manage payslips permission.

The Employee details card keeps identity and address context visible. The Timesheets card shows timesheets for the same user, week, and year, with recorded hours and travel totals. This gives payroll users a way to compare the payslip against work-history data before saving changes.
\subsection{Payslip Review Page}

The Payslip Review page is a simpler review queue than the full payslips list. It focuses on payslips pending review. The table shows employee name, period end, payout date, hours, net amount, status, and a download action. A Refresh button reloads the queue. Zero-hour on-call contract periods with no pay are skipped instead of creating empty payslips, while missing finalized contract data or missing timesheet data can still place a payslip into review.

The reviewer can download a PDF directly or click a row to open the management payslip detail page. This screen is useful when the reviewer wants a narrow queue of review items instead of the broader all-payslips filtering interface.

\section{Major User Roles}

\subsection{Employee}

An employee is an active user who mainly sees personal data and personal workflows. The employee can log in, reset their password, complete onboarding, use the User Dashboard, respond to shift requests, view accepted shifts, submit travel claims after completed shifts, view their own work history, request leave, download payslips, report payslip errors, send messages to the company inbox, and view personal account pages.

The employee experience is deliberately self-service. It does not expose company-wide user lists, planning management, role configuration, or payroll editing unless the user also has permissions for those areas.

\subsection{Permission-Based Management User}

A management user is any active user with at least one management permission. There is no separate frontend admin mode. A role named Admin may grant many permissions, but the frontend treats it the same way it treats every other role: it reads the permissions and builds the available UI from them.

This means a user can have broad management access or a narrow role. For example, one user might only manage planning, another might only review travel claims, and another might manage roles and company settings. Each user sees the same personal dashboard first, plus the Management entry and management pages their permissions allow.

\subsection{Planning Manager}

Planning access is represented by \code{CAN_MANAGE_PLANNING}. A user with this permission can open Planning and Clients from the Management area. They can view the planning calendar, create events, manage clients, create shifts, edit shifts, assign employees, remove employees from shifts, and re-invite declined employees.

From the frontend perspective, this role is centered on event staffing. The planner creates the structure of the work and then fills it with employees.

\subsection{Timesheet and Travel Claim Manager}

Timesheet management is represented by permissions such as \code{CAN_VIEW_ALL_TIMESHEETS} and \code{CAN_MANAGE_TIMESHEETS}. A user with all-timesheets access can view more than their own work history. A user with travel/timesheet management access can open Travel Claims and approve or reject pending claims.

This role sits between planning and payroll. The user can see whether shifts became timesheets, whether travel expenses were submitted, and whether those travel expenses have been reviewed.

\subsection{Payroll or Payslip User}

Payslip visibility is represented by \code{CAN_VIEW_PAYSLIPS} and \code{CAN_VIEW_ALL_PAYSLIPS}. Employees with payslip access can view and download their own payslips. Users with all-payslips access can inspect broader payroll lists. Users with \code{CAN_REVIEW_PAYSLIPS} can use the review queue, and users with \code{CAN_MANAGE_PAYSLIPS} can edit payslip fields, statuses, and deduction lines.

This role is about turning worked hours and payroll data into a document the employee can view, download, and question if something looks wrong.

\subsection{Company and Role Manager}

Company and access management is represented by permissions such as \code{CAN_MANAGE_COMPANY}, \code{CAN_CREATE_ROLE}, \code{CAN_ASSIGN_ROLES}, \code{CAN_REMOVE_ROLES}, \code{CAN_EDIT_ROLES}, and \code{CAN_DELETE_ROLES}. Users with these permissions can open Company settings, update company details, manage company logo, configure workflow behavior, and maintain roles and members.

The frontend treats this as a configuration role. It does not sit in the daily shift flow; instead, it defines how the rest of the app behaves and who can access which management screens.
\section{App Pipelines and Workflows}

\subsection{Login, Password Reset, and Access}

The user journey usually starts at the root URL or on the login page. The root URL is guarded and redirects active users to the dashboard, pending setup users to onboarding, and signed-out users to login. On the login page, the user enters credentials and submits the login form. The frontend then loads the current user, preserves the backend user status, refreshes permissions only for active users, and decides whether the user needs password reset, onboarding, a waiting-for-review state, or dashboard access.

Once the user is signed in, access rules keep the flow clean. A pending setup user is redirected to onboarding. A user with \code{PENDING_PROFILE_REVIEW} is redirected to onboarding and sees the waiting state instead of the normal dashboard, but can still open a direct \code{/contracts/:contractId/sign} contract signing link after management sends a contract email. A signed-out user is redirected to login. A user missing a required permission is sent back to dashboard. Management pages use permission guards such as \code{CAN_VIEW_USERS}, \code{CAN_MANAGE_PLANNING}, \code{CAN_MANAGE_TIMESHEETS}, \code{CAN_VIEW_ALL_PAYSLIPS}, and company or role permissions. This creates a guided path through the app instead of exposing pages the user cannot use.
\subsection{Employee Invitation and Onboarding}

An authorized user creates an employee from the Management Employee Onboarding page. They enter the employee's personal, contact, function, wage, contract, payment frequency, and travel allowance information. When the form is submitted, the frontend displays the generated username, temporary password, and email result.

The employee then logs in. If a password reset is required, that happens first. If the employee is still \code{PENDING_SETUP}, they are sent to the onboarding page. The employee completes the five-section private onboarding form with address, bank details, payroll and tax choices, ID verification metadata, front and back ID image uploads, and emergency contact details. When setup is finished, the employee moves to profile review and sees the onboarding waiting state until management reviews the profile. Management can review the submitted onboarding details and ID image from the employee profile, create a contract draft if one is missing, and then send the draft contract email to the employee. If a contract was already marked sent, management can resend the email from the active contract card. The email now tells the employee that their ParadePaard employment contract is ready to review and sign, and the Review and sign contract button opens the dedicated contract signing page. The employee reviews the document-style contract, checks the agreement box, types their full legal name, optionally draws a signature, and signs at the bottom of the page. Management then finalizes the signed contract through a similar employer signing panel, where the manager confirms the review, types their name, optionally draws a signature, and finalizes the contract. Management can also reject it with a comment.

The workflow starts with an authorized user creating the account and ends with a finalized contract. Finalization activates the employee for the normal application experience, where they can manage their own planning, work history, leave, travel claims, and payslips.

\subsection{Planning and Shift Assignment}

Planning starts on the Planning Overview page. The planner chooses a week or month, creates an event, attaches client and location information, and adds notes. The event appears in the calendar and can be opened in the event detail page.

Inside the event detail page, the planner creates shifts. A shift describes when work happens, what function is needed, where it happens, how many people are required, and how much break time applies. After shifts exist, the planner expands a shift and schedules employees from the available people list. A scheduled employee receives an assignment with status \code{ASSIGNED}.

The assignment then moves to the employee side. On the dashboard or My Planning page, the employee sees the request and accepts or declines it. Acceptance changes the status to \code{CONFIRMED}. Decline changes it to \code{CANCELLED}. The planner can see these states in the event detail page and can invite declined employees again.

\subsection{Working a Shift, Logging Hours, and Work History}

After a shift is accepted and worked, the frontend represents the outcome through timesheet and planning states. Company workflow settings determine whether timesheets are expected to be finalized manually by management or logged automatically after the shift ends. The employee sees the result as Scheduled, Pending log, or Logged.

Logged timesheets appear on the My Work History page for the signed-in employee. Managers with \code{CAN_VIEW_ALL_TIMESHEETS} use the separate Management Work History page to see all employees. A timesheet can be opened into a worked-shift detail page, where the user sees the project, shift, function, hours, break, logged time, and travel expense context.

The result of this workflow is a worked-hours record that can inform dashboards, management user details, travel claim review, and payroll.

\subsection{Travel Claims}

Travel claims start from the employee's shift detail page. The employee opens a completed shift, enters kilometers traveled, optionally uploads proof, and submits the claim. The UI calculates the claim amount using EUR 0.23 per kilometer unless an existing reviewed amount is already present.

If the company workflow requires approval, the claim enters the Travel Claims page. A manager opens that review queue, reviews the pending claim, views proof if available, and approves or rejects it. A rejection includes a reason. After review, the claim leaves the pending queue, and the employee can see the claim status and review note from shift and work-history detail pages.

\subsection{Leave Requests}

Leave starts on the User Dashboard. The employee clicks New Request, chooses the leave type, enters start and end dates, enters hours per day, chooses whether weekends should be skipped, and adds an optional note. The modal calculates total requested hours, current available hours, and remaining hours if the request is approved.

After submission, the leave request appears in the employee's leave list as \code{PENDING}. Authorized managers see pending leave requests in management review tooling. The manager opens the request, reviews dates, hours, available balance, remaining balance, and notes, then approves or rejects it. Approved leave reduces the employee's available leave hours shown on the dashboard.

\subsection{Payslip Review and Payslip Errors}

Payslips appear to employees in the dashboard and in the Payslips page. Employees can download PDFs and inspect details. If something looks wrong, the employee reports an error with a title and optional note. The payslip then becomes visible to payroll reviewers as disputed or needing attention. Scheduled payslip generation uses the finalized contract as the source for payment frequency and contract snapshot data.

Payroll users can open a payslip from the payslip review page or the all-payslips list. In the management payslip detail page, users with manage permission can review same-week timesheets, change status, edit error text, adjust pay details, edit deductions, and save. Empty on-call periods with no hours, no travel, and no net pay are skipped instead of producing a zero payslip. The employee-facing detail page then reflects the resulting payslip information.

This workflow connects worked hours, payroll review, employee dispute handling, and final PDF download into one frontend loop.

\subsection{Company Configuration}

Company configuration starts from the navbar company menu. An authorized user opens Company settings and moves between details, roles, and workflow tabs. Company details affect how the company is displayed. Roles and permissions affect who sees management pages. Workflow settings affect future timesheet and travel-claim behavior, while payslip timing is controlled by the binding contract elsewhere in the app.

The Roles and permissions tab now treats the built-in USER role as a protected employee self-service role. It can still be assigned to employees, but the role name, color, permission list, and delete action are locked in the role editor. This prevents normal employees from accidentally receiving management access while still keeping their own contract signing permissions available.

This workflow is less frequent than scheduling or payslips, but it defines the rules that make those daily workflows behave correctly.

\section{Navigation}

Navigation is split between the top navbar and the primary navigation. The top navbar gives global account actions. It starts with a top-left arrow button that returns to the previous page in the user's actual browser history. If there is no previous page, it falls back to the dashboard. This makes page-to-page movement consistent across the app, including when a user opens an employee profile from search or from another page that is not the Users list. The top navbar also shows the ParadePaard brand, user search when the user has \code{CAN_VIEW_USERS}, a company menu when the user has company or role permissions, and the user avatar menu. The user search now loads employee results on demand when the search field is opened, so the app does not preload the whole user directory on every screen. The avatar menu shows the signed-in name, links to Account, and supports logout.

The user search in the navbar is a fast path to employee detail pages for authorized users. A user types part of a name, preferred name, or email, and the dropdown shows up to eight matches. The results are loaded only when the search is opened, which keeps the header lightweight on pages that do not use search. Selecting a result opens that employee's Management User Detail page. The company menu opens Company Settings and is hidden from users without company or role-management permissions.

The primary navigation is permission-aware. Everyone gets Dashboard, My planning, Work history, Messages, and Account when those personal pages are available. Payslips appears only for users with own-payslip or all-payslip permission. Management appears only when the user has at least one management permission. Own-contract permissions, including the permission to sign a personal employment contract, do not count as management access. Inside Management, cards point only to the areas the user can access: users, applications, onboarding, onboarding review, contracts, planning, clients, work history, travel claims, payslip review, all payslips, and company settings. On desktop pages, the left navigation rail now stays fixed in place below the top navbar while the page content scrolls. This means the sidebar no longer shifts when the user reaches the bottom of a long page. The Messages icon can also show a small unread-count badge in its top-right corner, such as 1 or 2, when new company messages are waiting.

Access checks make the navigation rules enforceable. The root route is guarded and forwards users to the right first page: dashboard for active sessions, onboarding for pending setup, or login for signed-out visitors. Active pages require an active signed-in user. Onboarding is reserved for pending setup users. Permission-based pages require the matching permission. Old \code{/admin/...} URLs remain only as compatibility redirects into the new \code{/management/...} routes.
\section{Important Shared Components}

Cards are the main visual containers used throughout the app. A card usually has a title on the left, an optional action area on the right, and content below. Dashboards, account pages, planning pages, work history, payslips, and settings all use this structure.

Modals support focused tasks without leaving the current page. They are used for leave requests, leave decisions, payslip error reporting, event and shift editing, client editing, role editing, and similar tasks. When a modal is open, the page behind it is prevented from scrolling, which keeps the user's attention on the current task. The popup itself now stays inside the visible browser area and scrolls its content when the form is taller than the available space. Shared popups also leave a visible space below the top navbar, so the popup title bar does not sit directly against the navigation bar. This applies to shared popups such as creating or editing a role, creating events, editing shifts, and managing clients.

Pagination controls appear on pages with larger result sets, such as users, clients, payslips, and work history. They show previous and next buttons, numbered pages with ellipses when needed, and a results-per-page selector.

Back buttons give detail pages and account pages a consistent way to return. They now use the previous browser page first and only use their configured route when the page was opened directly with no previous page available. The visible label is kept generic as Back, because the destination depends on where the user actually came from.

Loading indicators appear while access is checked, while dashboards fetch data, and while detail pages load records.

The leave request modal is one of the most important shared workflow components. It turns dates, hours per day, weekend skipping, and available balance into a clear leave summary before submission. The management request modal mirrors that logic for decision-making by showing requested hours, available hours, and remaining balance if approved.

Planning labels are kept consistent across the app. A scheduled request is shown as Scheduled, an accepted assignment is shown as Accepted, and a declined assignment is shown as Declined. The same shared behavior also produces required, scheduled, and checked-in staffing labels and visual staffing tones.

\section{Important States and Statuses}

The user status controls the first major branch in the app. A user with \code{PENDING_SETUP} is not allowed into the active application and is sent to onboarding. After setup, the user can move through review states such as \code{PENDING_PROFILE_REVIEW}, \code{CHANGES_REQUESTED}, \code{PENDING_CONTRACT_SIGNATURE}, and \code{PENDING_CONTRACT_REVIEW}. A user with \code{ACTIVE} status can use protected app pages.

Leave requests use the familiar review states. \code{PENDING} means the employee submitted the request and is waiting for a manager decision. \code{APPROVED} means the request was accepted and the hours count against the leave allowance. \code{REJECTED} means the request was denied. The shared types also include \code{CANCELED}, although the visible flow mainly centers on pending, approved, and rejected.

Planning assignments describe the employee's answer to a planned shift. \code{ASSIGNED} is a scheduled request waiting for response. \code{CONFIRMED} is an accepted shift. \code{CANCELLED} is a declined or canceled assignment. The UI labels these as Scheduled, Accepted, and Declined.

Planning staffing states describe whether an event or shift has enough people. Empty means nobody is scheduled. Partial means some people are scheduled but the requirement is not met. Staffed means the scheduled count meets or exceeds the required count. Finalized means the event is locked and planning actions are disabled.

Timesheet states are shown in employee planning and work history. Scheduled means a future accepted shift has not become a timesheet. Pending log means a past accepted shift has not been logged yet. Logged means the assignment has been exported or recorded as a timesheet. Management timesheet history also displays created timesheets as Recorded.

Travel claim states explain expense review. Not submitted means no claim exists. Pending means the employee submitted a claim and it awaits review. Approved means the claim was accepted. Rejected means the claim was denied and may include a review note.

Payslip statuses drive the payroll review experience. \code{PENDING_REVIEW} is waiting for payroll review. \code{NEEDS_ATTENTION} marks a payslip that requires payroll work. \code{DISPUTED} means the employee reported an issue or the payslip is being challenged. \code{RELEASED} means the payslip is available to the employee. \code{APPROVED} means it has been accepted. \code{NOT_ACCEPTED} is a frontend filter used to find payslips that are not released or approved.

Contract statuses drive contract-owned payroll. \code{DRAFT} is a contract being prepared. \code{SENT_TO_EMPLOYEE} means the employee can view and sign it, and management can resend the contract email if needed. \code{EMPLOYEE_SIGNED} means it is waiting for management review. \code{FINALIZED} means it can be used for payroll. \code{REJECTED} means management sent it back with a comment. \code{SIGNED} remains visible for older contract rows.

Workflow settings define how future operational states are created. \code{ADMIN_FINALIZE} means timesheet logging depends on a manual management finalization step. \code{AUTO_ON_SHIFT_END} means timesheets can be created automatically after a shift ends. \code{REQUIRES_APPROVAL} means travel claims wait for review. \code{AUTO_APPROVE} means travel claims can be accepted automatically. Payslip cadence is not exposed in this workflow section because it follows the contract binding instead.

\section*{Change Log}

\begin{itemize}
    \item 2026 05 28: Let the onboarding review page update an existing draft contract so wage and other contract setup edits can be saved without creating a second contract.
    \item 2026 05 27: Added contract PDF download actions to the onboarding review queue and to the final review section after a draft or current contract exists.
    \item 2026 05 27: Updated the onboarding review travel allowance note so it shows the current EUR 0.23 net per kilometer rate directly on the page.
    \item 2026 05 27: Moved travel allowance guidance to the Horeca Payroll and Contract Rules flow and updated onboarding and contract text to point to that shared rules page.
    \item 2026 05 27: Reworked the Horeca job preset popup so it uses the same dark tabbed wizard UI as Create project.
    \item 2026 05 27: Removed the payslip timing field from Company settings so the workflow tab only controls timesheets and travel claims.
    \item 2026 05 27: Moved the manual wage override reason directly under the gross hourly wage field in the Horeca Payroll and Contract Rules page so the wage and reason stay visually grouped.
    \item 2026 05 27: Removed the commercial payroll billing rate field from the Horeca Payroll and Contract Rules page so the contract section only shows the operational payroll setup inputs.
    \item 2026 05 27: Added a short travel allowance explanation to the onboarding review contract setup section so the page clarifies that the amount is controlled by company policy.
    \item 2026 05 27: Removed the payroll billing rate field from the onboarding review contract setup section so the page focuses on employee and contract review inputs.
    \item 2026 05 27: Updated the Onboarding Review identification section so admins can open both the front and back ID document uploads.
    \item 2026 05 26: Stopped service startup seed data from deleting accepted onboarding users, auth accounts, role links, and contracts after a rebuild or restart.
    \item 2026 05 26: Fixed onboarding review contract creation so Full time, Part time, and Zero hours choices save as valid contract types.
    \item 2026 05 26: Updated the Messages and Management Messages descriptions after fixing the live message stream so open inboxes no longer block other user and account pages.
    \item 2026 05 26: Reduced always-on navbar user loading by making employee search load on demand and deduplicating shared frontend read requests.
    \item 2026 05 26: Let the onboarding ID upload boxes accept PDF files as well as images and changed the picker button text to Choose file.
    \item 2026 05 26: Added Dutch-style placeholder examples to the public application name fields so applicants can see how to enter full first names, preferred name, prefix, and surname.
    \item 2026 05 26: Made the onboarding ID image upload route accept both the front/back multipart shape and the older single-file multipart shape so uploads do not fail on mismatched builds.
    \item 2026 05 26: Changed the onboarding ID issue and expiration date fields to auto-format as dd/mm/yyyy while still submitting valid backend dates.
    \item 2026 05 26: Fixed the onboarding ID upload picker styling so the centered button and filename layout overrides the generic setup form label styling.
    \item 2026 05 26: Centered the onboarding ID upload button inside each box and moved the selected filename directly underneath it.
    \item 2026 05 26: Adjusted the onboarding ID upload boxes so the button and filename are centered in the same CV-style control while keeping the front and back boxes side by side.
    \item 2026 05 26: Made the onboarding ID upload controls match the apply-page CV picker style while keeping the front and back boxes side by side.
    \item 2026 05 26: Updated the employee onboarding ID verification step to use separate front and back upload boxes and store both sides of the ID.
    \item 2026 05 26: Removed the pension participant and special Zvw contribution options from the onboarding setup step.
    \item 2026 05 26: Fixed the public application submit request so the browser can send the multipart upload with the correct boundary through the gateway.
    \item 2026 05 26: Split Work History into a personal My Work History page and a permission-protected Management Work History page with flexible filters and saved management columns.
    \item 2026 05 25: Added an unread-count badge to the Messages icon in the primary navigation.
    \item 2026 05 25: Fixed the desktop primary navigation sidebar so it stays in a fixed position while long pages scroll.
    \item 2026 05 25: Simplified Payroll Finance to an accurate overview-only page, removed the fake approved payroll run details, and cleaned startup seed data so the app starts with only the Sanne admin login.
    \item 2026 05 25: Added payroll finance permissions to the auth seed, admin permission set, super-admin permission coverage, and role permission grouping so eligible users can see the Payroll Finance management card.
    \item 2026 05 25: Changed Payroll Finance into an approved-payroll-run summary page and added configurable Work History columns with finance-only values hidden behind payroll finance permission.
    \item 2026 05 25: Restored the separate Calendar and List selector on the Planning Overview so it works independently from the Shifts and Projects tabs.
    \item 2026 05 25: Added Shifts and Projects tabs to the Planning Overview, defaulted the page to Shifts, and made the Projects tab use the list-style view.
    \item 2026 05 25: Fixed the Planning Overview page so newly created projects without shifts no longer cause a white screen, and updated the page description.
    \item 2026 05 23: Added the Payroll Finance management page for internal shift billing, employer cost, client revenue, and margin review.
    \item 2026 05 23: Simplified the horeca payroll calculator so users enter employee and contract details while the app derives tax, pension, holiday allowance, and employer contribution values automatically.
    \item 2026 05 23: Replaced the horeca example payroll table with a payroll calculator, removed the company tax settings tab, and removed the separate CAO templates management area.
    \item 2026 05 23: Fixed popup overlays so the full screen dims and blocks background clicks, and improved the horeca job preset popup text and field contrast.
    \item 2026 05 23: Changed horeca job preset management so preset creation and editing use a popup form and the preset table uses symbol actions for edit, enable or disable, and delete.
    \item 2026 05 23: Fixed Planning service exports so the Planning Overview page can load again after the Event to Project rename (restored missing CreatePlanningEvent and getEvent helper exports).
    \item 2026 05 23: Fixed the Management Planning Event Detail route so opening an event detail page no longer fails due to a missing frontend page import.
    \item 2026 05 23: Added the Horeca Payroll and Contract Rules management page and updated the onboarding review contract setup to use source-based horeca job presets, wage validation, payroll settings, and source details.
    \item 2026 05 21: Added a Calendar view or List view selector to Planning Overview so planners can switch between the grid and a day grouped list.
    \item 2026 05 21: Updated the Planning Overview Plan someone in panel to search employees on demand (no full user list), keep selected people visible as chips, and allow horizontal scrolling for long names.
    \item 2026 05 21: Tightened the My planning spacing so the table header sits directly under the card header, and updated the My Planning page accepted list to use the same table styling.
    \item 2026 05 21: Tightened the My planning dashboard table spacing so the header and rows use the full card width.
    \item 2026 05 21: Improved the My planning dashboard rows with clearer hover/focus styling and a status pill.
    \item 2026 05 21: Simplified the dashboard My planning card by removing the per-day header and using a single scrollable shift list.
    \item 2026 05 21: Moved the Payslip Detail Back control into the page header so it matches the rest of the app.
    \item 2026 05 21: Updated the Payslip Detail page so the cards use a list view layout instead of field tiles.
    \item 2026 05 21: Made Planning Overview default to Shifts mode and added selectable shift cards with a compact pop up action menu and bulk Plan someone in panel.
    \item 2026 05 21: Updated the planning shift selection + popover design spec to re-invite existing assignments when planning people in bulk (no UI change yet).
    \item 2026 05 21: Added a Planning Overview shift selection + popover actions design spec (no UI change yet).
    \item 2026 05 20: Updated the My Planning page so scheduled shifts only appear as response cards when a shift needs acceptance or decline.
    \item 2026 05 20: Added a My Planning scheduled-shift response card design note (no UI change yet).
    \item 2026 05 20: Removed the manual Refresh button from the user Messages page because the thread updates live.
    \item 2026 05 20: Updated the onboarding review Save review action to also store section checkmarks and contract setup draft fields so a review can be resumed later.
    \item 2026 05 20: Fixed the onboarding review Save review actions so Request changes saves the correct decision, Ready to send contract moves the employee to Contract review, and sending the contract moves the employee to Awaiting signature.
    \item 2026 05 20: Fixed contract draft creation by aligning the contract type dropdown values with the backend (Fixed hours, On-call Runner, On-call Bar).
    \item 2026 05 19: Removed the collapse, refresh, and close controls from the shared admin inbox UI.
    \item 2026 05 19: Removed the Messages card from the Management dashboard.
    \item 2026 05 19: Made the user and admin Messages inbox update live so new incoming messages appear automatically without a manual page refresh.
    \item 2026 05 19: Restored the shared top navigation bar on the Messages pages so they match the layout of the other pages.
    \item 2026 05 19: Blocked the onboarding review Create and send contract action until every review section checkbox is checked.
    \item 2026 05 19: Made completed onboarding review section headers turn green when the section checkbox is checked.
    \item 2026 05 19: Moved the onboarding review checklist card to the end of the page so it acts as a final status summary.
    \item 2026 05 19: Added a read-only review checklist card that turns checklist items green when their section checkbox is marked complete.
    \item 2026 05 19: Moved onboarding review completion checkboxes onto each review section header and removed the separate checklist card.
    \item 2026 05 19: Fixed the onboarding review checklist layout so the checkbox and section label render on one clean line.
    \item 2026 05 19: Updated the onboarding review checklist rows to use simple checkboxes (no buttons or extra status dots).
    \item 2026 05 19: Simplified the onboarding review checklist to checkbox-only rows and removed the extra status pills.
    \item 2026 05 19: Refined the onboarding review checklist visuals and spacing so checklist items are clearly checkable and do not sit against card edges.
    \item 2026 05 19: Added manual checklist checkboxes to the onboarding review page so admins can mark each section complete once required fields are filled.
    \item 2026 05 19: Made onboarding review contract setup require role/function selection and an end date, and improved checklist status pills with clearer complete markers.
    \item 2026 05 19: Changed onboarding review contract setup dates to use dd/mm/yyyy input with auto formatting while typing.
    \item 2026 05 19: Moved the onboarding review checklist below the review sections so it appears at the end of the form.
    \item 2026 05 19: Added padding inside onboarding review form cards so the fields do not sit against the edges.
    \item 2026 05 19: Added extra padding around the management onboarding review detail form for better spacing.
    \item 2026 05 19: Redesigned the management onboarding review flow with a dedicated Onboarding Review detail form, checklist, and contract setup section.
    \item 2026 05 19: Updated the employee onboarding ID document image picker to match the styled CV upload control.
    \item 2026 05 18: Fixed the employee onboarding ID document upload so pending setup users are not blocked by missing token permissions.
    \item 2026 05 18: Added spacing between the accepted application closed-decision message and the resend decision email button.
    \item 2026 05 18: Changed the accepted application resend action so it sends an account setup email instead of a password reset email.
    \item 2026 05 18: Added a resend decision email action for accepted applications so reviewers can send a fresh password setup email.
    \item 2026 05 18: Removed a personal email address from a sample user-service update request; no frontend behavior changed.
    \item 2026 05 18: Updated the public application flow so duplicate applicant emails are rejected and shown as an error on the apply form.
    \item 2026 05 18: Made the admin messages drawer close automatically when the company menu or account menu is opened.
    \item 2026 05 18: Moved the admin shared messages inbox into a right-side drawer with a navbar icon and made selected user chats fill the message box.
    \item 2026 05 18: Fixed the user-service startup seed script so existing application databases without the old availability notes column can start correctly.
    \item 2026 05 18: Added a user Messages page and a shared Management Messages inbox where admins can reply to one ongoing company conversation per user.
    \item 2026 05 17: Fixed the public application submission route so the apply form can submit through the API gateway without requiring login.
    \item 2026 05 17: Aligned the backend application API with the simplified public application form by replacing the old background fields with one applicant note field.
    \item 2026 05 17: Simplified the public application form by removing extra background fields, adding one Note section, improving the CV upload control, and aligning checkboxes before their labels.
    \item 2026 05 17: Made the public application date fields add dd/mm/yyyy slashes automatically while the applicant types.
    \item 2026 05 17: Changed the public application date of birth and availability start date fields to use the dd/mm/yyyy format.
    \item 2026 05 17: Renamed the public application form middle name prefix label to Prefix.
    \item 2026 05 17: Aligned onboarding review permissions so reviewers can open submitted profiles and made the user detail page load the most relevant draft or signed contract for follow-up actions.
    \item 2026 05 17: Finished the accepted-applicant review path with complete application fields, reviewer onboarding evidence, ID document download, and contract draft creation before contract signing.
    \item 2026 05 17: Fixed the onboarding ID upload retry path so the image uploads before setup completion and upload errors stay inside the onboarding form.
    \item 2026 05 17: Expanded the employee onboarding page with bank details, payroll and tax choices, ID verification upload, emergency contact details, and a waiting-for-review state.
    \item 2026 05 17: Expanded accepted-applicant onboarding data for payroll, ID verification, bank holder details, and emergency contacts.
    \item 2026 05 17: Kept the application decision feedback visible after accepting or denying an applicant, including the pending manual email warning.
    \item 2026 05 17: Added protected application review screens where permitted users can view submitted applications, download a CV, and accept or deny applicants.
    \item 2026 05 17: Added the public application page where applicants can submit basic details, work interest, consent, and an optional CV before sensitive onboarding.
    \item 2026 05 17: Added frontend service types and API wrappers for public applications and application review; no visible application screens changed yet.
    \item 2026 05 17: Added a guarded placeholder route for the Applications management card so the new navigation target opens correctly.
    \item 2026 05 17: Added application review permissions to the management navigation policy; no visible application screens are available yet.
    \item 2026 05 17: Added a decision lock to the application acceptance flow so repeated accepts cannot start duplicate onboarding work; no frontend behavior has changed yet.
    \item 2026 05 17: Hardened application review API errors, decision states, and public-route security tests; no frontend behavior has changed yet.
    \item 2026 05 17: Made the public application endpoint accessible without login and hardened accepted application user creation; no frontend behavior has changed yet.
    \item 2026 05 17: Added backend endpoints for public application submission and application review decisions; no frontend behavior has changed yet.
    \item 2026 05 17: Added the backend application domain model for the upcoming public application flow; no frontend behavior has changed yet.
    \item 2026 05 17: Added an implementation plan for the public application, application review, accepted-applicant onboarding, and contract follow-up flow; no frontend behavior has changed yet.
    \item 2026 05 17: Added a design spec for a public application page, protected application review queue, accepted-applicant onboarding, and the follow-up contract workflow; no frontend behavior has changed yet.
    \item 2026 05 16: Fixed service startup seed data so existing users, roles, and company settings can migrate without blocking the frontend.
    \item 2026 05 15: Locked finalized contract PDF downloads so the employer signature stays in the stored final document.
    \item 2026 05 15: Changed contract finalization into an employer signing flow and separated employer and employee signature blocks in the PDF.
    \item 2026 05 15: Fixed Contract PDF download so sent contracts with an older cached PDF are regenerated before download.
    \item 2026 05 15: Removed a personal email address from sample requests and contract tests; no frontend behavior changed.
    \item 2026 05 15: Updated contract PDF downloads so they use the current employment agreement text and include the employee signature at the bottom.
    \item 2026 05 15: Locked the built-in USER role to employee self-service permissions so employees can sign their own contracts without seeing Management or the Contracts workspace.
    \item 2026 05 15: Fixed employee contract signing so the owner of a sent contract can sign even when their token is missing the sign-contract permission.
    \item 2026 05 15: Fixed resent contract emails and old nested contract links so they open the dedicated contract signing page.
    \item 2026 05 14: Added a dedicated contract signing page, updated the contract email button, and changed Employment Details to open the review-and-sign flow.
    \item 2026 05 14: Updated contract sending so the active contract card sends or resends a contract email and shows an error if delivery fails.
    \item 2026 05 14: Changed the forgot-password return link from Back to login to the generic Back wording.
    \item 2026 05 14: Added a Planning Overview search field for filtering the current planning by assigned user, client, or event.
    \item 2026 05 14: Fixed current contract loading after contract PDFs have been generated, and updated the contract page descriptions.
    \item 2026 05 14: Removed the extra Back to work history button from the Travel Claims page so the page only uses the standard Back control.
    \item 2026 05 14: Added an app-wide top-left back arrow and changed page back controls to return to the user's previous page first.
    \item 2026 05 13: Fixed the Docker service connection used for contract PDF downloads so the contract service can fetch employee profile data.
    \item 2026 05 13: Added dedicated onboarding review and contracts management pages so those Management cards no longer open generic pages.
    \item 2026 05 13: Fixed the employee onboarding finish flow so setup can move the user into profile review without a bad-request error.
    \item 2026 05 13: Separated the house number and suffix input cells on the employee onboarding address step.
    \item 2026 05 13: Updated password reset and employee onboarding email delivery to use the MailerSend Email API configuration.
    \item 2026 05 12: Documented the styled travel-claim layout on the My Planning Shift Detail page and added the latest project instruction and timeline files.
    \item 2026 05 12: Added contract-owned payment frequency, employee contract visibility, contract signing status, management contract review actions, and payroll review behavior.
    \item 2026 05 12: Added an implementation plan for the contract-owned payroll and onboarding workflow; no frontend behavior has changed yet.
    \item 2026 05 12: Added a contract-owned payroll and onboarding workflow design spec; no frontend behavior has changed yet.
    \item 2026 05 11: Added shared spacing between popup title bars and the top navigation bar.
    \item 2026 05 11: Made the Management Dashboard cards clickable and removed the separate Open buttons.
    \item 2026 05 11: Updated My Planning so ended shifts stay off the dashboard and remain available from the full My Planning Past tab.
    \item 2026 05 11: Added Back to management arrow controls to the main management work pages.
    \item 2026 05 11: Removed the arrow from the Management Dashboard card Open actions.
    \item 2026 05 11: Removed the single-letter markers from the Management Dashboard cards.
    \item 2026 05 11: Refined the Management Dashboard cards with grouped sections, clearer descriptions, and stronger Open actions.
    \item 2026 05 11: Updated the Planning Overview page so the day cells stretch to the bottom of the visible planning area.
    \item 2026 05 07: Made shared popups scroll inside the visible browser area, including the create role popup.
    \item 2026 05 07: Grouped role permission checkboxes into clear sections in the create and edit role modals.
    \item 2026 05 07: Reworked the frontend from an admin flow to a permission-based personal dashboard and Management flow.
    \item 2026 05 07: Added the implementation plan for changing the frontend from an admin flow to a permission-based My Work and Management flow.
    \item 2026 05 07: Added a permission-based role-flow design spec; no frontend behavior has changed yet.
\end{itemize}

\section{Final Summary}

The ParadePaard frontend tells one connected workforce story. An authorized user invites an employee and sets up the first contract details. The employee logs in, resets their password if needed, completes onboarding, and starts using the personal dashboard. A planner creates events and shifts, then assigns employees. Employees accept or decline those shifts. Completed shifts become worked-hour records, and those records appear in work history. Travel claims can be submitted after completed shifts and reviewed by managers. Worked hours, travel amounts, tax settings, and payroll review come together in payslips. Employees can download payslips or report errors, and payroll users can investigate and correct them when their permissions allow it.

The app is now held together by permission-aware navigation and page protection instead of a separate admin flow. Every active user starts with their own work area. Management pages appear only when the user's role grants the matching permissions. A broad Admin role can still exist, but it is only one possible permission bundle. The frontend therefore works as both an employee self-service portal and a flexible management console, with planning and payroll acting as the bridge between the two.
\end{document}
